Linting Linearity in Core/System FC

### 2023-01-09 report.tex
Extend linear types introduction story

Linear type systems\cite{} add expressiveness to existing type systems by
defining that linear resources must be used exactly once (linearly). In
programming languages with a linear type system, not using certain resources or
using them twice are type errors. Linear types can, thus, be used, e.g., to
guarantee file handles, socket descriptors and allocated memory are freed
exactly once (leaks and double-frees become type errors)\cite{}, implement safe
high-performance language interop\cite{}, guarantee quantum entangled states are
not duplicated~\cite{}, handle mutable state\cite{}, a bit on session
types guarantees\cite{}, and much more.

@@

As an example, consider the following program which allocates some memory and
frees it twice. The variable $p$ is a linear resource created by the
\textbf{malloc} keyword.

@@

Because $p$ is a linear variable, it must be used exactly once. However, we are
using it in both calls to \textbf{free}. The example program doesn't typecheck!
In section~\ref{linear-types} we describe the fundamentals of linear types in
more detail with a formal definition and many examples.

Despite their usefulness, most mainstream programming languages don't have
linear types. In practice, it can be hard to balance linear and non-linear types
and avoid the boilerplate threading of linear resources that we'll see ahead.

>>>>

Linear type systems\cite{} add expressiveness to existing type systems by
stating that linear resources must be used exactly once (linearly). In
programming languages with a linear type system, not using certain resources or
using them twice are type errors. Linear types can, thus, be used to, e.g.,
guarantee that file handles, socket descriptors, and allocated memory are freed
exactly once (leaks and double-frees become type errors)\cite{}, implement safe
high-performance language interoperability\cite{}, guarantee that quantum
entangled states are not duplicated~\cite{}, handle mutable state\cite{},
something on session types guarantees\cite{}, and much more.

@@

As an example, consider the following linearly typed program which allocates
some memory and frees it twice. The variable $p$ is a linear resource created by
the \textbf{malloc} keyword.

@@

Because $p$ is a linear variable, it must be used exactly once. However, we are
using it in two different calls to \textbf{free}. The example program
\emph{doesn't typecheck}! In section~\ref{linear-types} we describe the
fundamentals of linear types in more detail with a formal definition and many
examples.

Despite their great promise and research literature, few programming languages
have linear types --
% , with Rust\cite{} (with its ownership types), Idris\{}, and recently
% Haskell\cite{} being the most popular.
it is hard to balance linear and non-linear types in a pratical language. Linear
Haskell\cite{linearhaskell} tackles this difficulty and describes a type system
to retrofit linear types into Haskell, a purely-functional lazy language, while
retaining backwards-compatibility and code reuse across linear and non-linear
users of libraries.
% , and, e.g., avoid the required boilerplate threading of linear resources that we will get to know ahead.

% In an attempt to bridge the gap between the theory and practicality of linear
% types, Linear Haskell\cite{} describes , the 9.0 version series of Haskell's
% \emph{de facto} compiler, GHC, supports linear types. However, retrofitting
% linear types to a purely-functional lazy language
